DNSKEY Management

### 2012-12-05 paper/paper.tex
trust chain progress. may need to finish it more nicely

By signing the keys of the TLD's, the root will put its trust into their keys, and any keys the TLD's have signed, resulting in a trust hierarchy illustrated in \ref{fig:trust-chain}. This way, a resolver querying EPFL's DNS server will be able to verify the received query answer against the known root-authority in the following way:

>>>>

By signing the keys of the TLD's, the root will put its trust into their keys, and any keys the TLD's have signed, resulting in a trust hierarchy illustrated in fig.~\ref{fig:trust-chain}. This way, a resolver querying the LACAL's DNS server for \verb|lacal.epfl.ch| will be able to verify the received query answer against the known root-authority in the following way:

\begin{enumerate}
\item Verify the reply's authenticity using \verb|lacal.epfl.ch|'s public key, obtained from \verb|epfl.ch|'s DNS server ;
\item Verify the query -- containing \verb|lacal.epfl.ch|'s public key -- returned by \verb|epfl.ch| with its public key, retrieved from the \verb|.ch| DNS server;
\item Again, verify \verb|.ch|'s responses by getting its public key from the root domain.
\item Finally, the root domain's responses can be verified with its already known public key.
\end{enumerate}
